---
title: "PSTAT131HW#2"
output:
  pdf_document: default
  html_document: default
date: '2022-04-06'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
library(tidyverse)
library(tidymodels)
abalone.data <- read.csv('C:/Users/arthu/Dropbox/My PC (DESKTOP-9BV8I37)/Desktop/abalone.csv.csv')
set.seed(43)
```
1) 

```{r}
abalone.data$age <- abalone.data$rings +1.5
ggplot(abalone.data, aes(x=age)) +
  geom_histogram(bins=30) +
  scale_x_continuous(breaks=seq(0, 30, 2)) +
  geom_vline(aes(xintercept=mean(age)), col='green')
```
This is clearly a right skewed distrbution with finding out the the mean is around 12 with a standard deviation around 3

2) 
```{r} 
p <- 0.7
strats <- abalone.data$type

rr <- split(1:length(strats), strats)
idx <- sort(as.numeric(unlist(sapply(rr, function(x) sample(x, length(x) * p)))))

train <- abalone.data[idx, ]
test <- abalone.data[-idx, ]
```

3) 
```{r}
train <- train %>% na.omit()
recipe_normal <- 
  recipe(age ~ type + longest_shell + diameter + height + whole_weight + shucked_weight + viscera_weight + shell_weight, data = train) %>%
  step_dummy(type, one_hot = F) %>%
  step_interact(terms = ~starts_with('type'):shucked_weight)
  step_interact(recipe_normal, terms = ~longest_shell:diameter)
  step_interact(recipe_normal, terms = ~shucked_weight:shell_weight)
  step_center(recipe_normal) %>% 
  step_scale(recipe_normal)
  
```

4)
```{r}
lm_model <- linear_reg() %>% 
            set_engine('lm') %>% 
            set_mode('regression')

```

5) 
```{r}
abalone_workflow <- workflow() %>% 
                        add_model(lm_model) %>% 
                        add_recipe(recipe_normal)
```

6) 
Use your fit() object to predict the age of a hypothetical female abalone with longest_shell = 0.50, diameter = 0.10, height = 0.30, whole_weight = 4, shucked_weight = 1, viscera_weight = 2, shell_weight = 1.

```{r}
abalone_fit <- abalone_workflow %>% 
                   fit(train)
predict.sample <- list(longest_shell = .5,
                       diameter = .10,
                       height = .3,
                       whole_weight = 4,
                       shucked_weight =1,
                       viscera_weight = 2,
                       shell_weight =1,
                       type = 'F')
predict.sample <- as.data.frame(predict.sample)
predict(abalone_fit, predict.sample) %>% unlist() %>% unname()
```
7) 
```{r}
library(yardstick)
multimetric = metric_set(rsq, rmse, mae)
boundtestdata = bind_cols(predict(abalone_fit, train),
                            train$age)
colnames(boundtestdata) = c("Predicted Age", "True Age")
multimetric(data=boundtestdata,
             truth="True Age",
             estimate="Predicted Age")
```
Looking at the values provided we can see that we get an R^2 value of 0.54 which represents that our model performs very poorly in having the response predicted by the predictor variables. 





```